---
title: "`r thetitle`"
date: "`r Sys.Date()`"
output: 
  html_document
    
params:
  all_seq_table_csv: ""
---
<style>

  #table-of-contents h2 {
    z-index: 200;
    background-color: #339966;
    text-align: center;
    padding: 0.809em;
    display: block;
    color: #fcfcfc;
    font-size: 100%;
    margin-top: 0px;
    margin-bottom: 0.809em;
  }

  h1, h2, h3, h4, h5, h6, legend {
    font-family: "Roboto Slab","ff-tisa-web-pro","Georgia",Arial,sans-serif;
    font-weight: 700;
    color: #339966;
  }
  
  #content {
    max-width: 100%;
  }
  
  .container-fluid.main-container {
    max-width: 100%;
  }
  
  .dataTables_length {
    padding: 10px;
  }
  
  
</style>


``` {r functions, include = FALSE}
library("knitr")
library("shiny")
library("DT")
library("tidyverse")
library("plotly")

all.seq.table = read.csv(params$all_seq_table_csv, stringsAsFactors = FALSE)
all.seq.table$classification = toupper(all.seq.table$classification)

if (max(all.seq.table$steps)=="6") {
  all.seq.table = subset(all.seq.table, chosen=="1")
}

all.seq.table$chosen = NULL


```


## Assemblies description

```{r donut_chart_one, echo=FALSE}
colors <- c(GOOD = 'rgb(0,128,255)', BAD = 'rgb(204,0,0)', `EMPTY WELL` = 'rgb(255,255,255)', PROBLEMS_IN_ASSEMBLY = 'rgb(102,0,0)')
colors_classif <- c(non_functional = 'rgb(255,255,255)', missing_ltr_or_psi = 'rgb(204,0,0)', intact = 'rgb(0,153,0)', msd_mutation = 'rgb(255,128,0)', duplications_or_inversion = 'rgb(153,41,255)', missing_internal_genes = 'rgb(160,160,160)')

data1 <- all.seq.table %>%
  group_by(classification) %>%
  summarize(count = n())

p1 <- plot_ly()  %>%
  add_pie(data = data1, hole = 0.6, labels = ~classification, values = ~count, marker = list(colors = colors[as.character(data1$classification)], line = list(color = '#000000', width = 1)) ) %>%
  # add_annotations(text = "Assemblies", x = 0.5, y = 1, yref = 'paper', xref = "x1", showarrow = FALSE, font = list(size = 15)) %>%
  add_annotations(text = ~ paste0('<b>', sum(data1$count), '</b>'), x = 0.5, y = 0.5, yref = "paper", xref = "x1", showarrow = FALSE, font = list(size = 40, color = toRGB("black") )) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5),
         showlegend = TRUE,
         title = list(text=sprintf("<b>%s</b>", "Assemblies") ),
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE)
  ) 

if (max(all.seq.table$steps) == "6") {
  
  data2 <- all.seq.table %>% 
    filter(classification == "GOOD") %>%
    group_by(final_classification) %>%
    summarize(count = n())
  
  p2 <- plot_ly()  %>%
    add_pie(data = data2, hole = 0.6, labels = ~final_classification, values = ~count, marker = list(colors = colors_classif[as.character(data2$final_classification)], line = list(color = '#000000', width = 1)) ) %>%
    # add_annotations(text = "Good Assemblies Classification", x = 0.5, y = 1, yref = "paper", xref = "x1", showarrow = FALSE, font = list(size = 15) ) %>%
    add_annotations(text = ~ paste0('<b>', sum(data2$count), '</b>'), x = 0.5, y = 0.5, yref = "paper", xref = "x1", showarrow = FALSE, font = list(size = 40, color = toRGB("black") )) %>%
    layout(legend = list(orientation = "h", xanchor = "center", x = 0.5),
           showlegend = TRUE,
           title = list(text=sprintf("<b>%s</b>", "Good Assemblies Classification") ),
           xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
           yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE)
    )
  

  
  fluidPage(
    fluidRow(
      column(4, p1), column(4, offset=3, p2)
    )
  )
  
} else {
  
  fluidPage(
    fluidRow(
      column(4, p1)
    )
  )
  
}

```




## Assemblies summary
Click on CSV or Excel to download the table.

```{r summary_passed, echo = FALSE, message = FALSE, warning=FALSE}

assemblies.summary.table = subset(all.seq.table, classification %in% c("GOOD","BAD"))

datatable(assemblies.summary.table,  
          extensions = 'Buttons',
          options = list( searching = TRUE, 
                          pageLength = 5, 
                          lengthMenu = c(5, 10, 15, 20), 
                          scrollX = TRUE, 
                          dom = 'Bfrtipl', 
                          buttons = c('csv', 'excel')
                          )
          )

```

## Problems in assembly
``` {r summary_failed_assembly, echo = FALSE}

problems.in.assembly.table = subset(all.seq.table, classification == "PROBLEMS_IN_ASSEMBLY")

datatable(problems.in.assembly.table, 
          extensions = 'Buttons',
          options = list( searching = TRUE, 
                          pageLength = 5, 
                          lengthMenu = c(5, 10, 15, 20), 
                          scrollX = TRUE, 
                          dom = 'Bfrtipl', 
                          buttons = c('csv', 'excel')
                          )
          )
```

## Empty wells summary

``` {r summary_failed, echo = FALSE}

empty.wells.table = subset(all.seq.table, classification=="EMPTY WELL")

datatable(empty.wells.table, 
          extensions = 'Buttons',
          options = list( searching = TRUE, 
                          pageLength = 5, 
                          lengthMenu = c(5, 10, 15, 20), 
                          scrollX = TRUE, 
                          dom = 'Bfrtipl', 
                          buttons = c('csv', 'excel')
                          )
          )
```



